\thispagestyle{empty}
\begin{center}
    \vspace*{\fill}
    Edition 0.3.0, 2024
    
    \textit{Copyright © 2024 by Sebastián Bobadilla Suárez}

Some rights reserved. This work is licensed to promote open scholarly discourse while protecting intellectual property rights. Readers are granted permission to: 1) Quote, cite, and reference this work in academic and scholarly contexts with proper attribution, 2) Use figures, tables, and excerpts for educational purposes with appropriate citation, 3) Share and discuss the ideas presented herein in academic discourse and reviews, and 4) Create derivative works that build upon these ideas in scholarly contexts.

The following restrictions apply: 1) Commercial use or reproduction of this work in its entirety requires prior written permission from the author, 2) Any substantial reproduction must include this copyright notice, 3) Attribution must be given to the author in all cases of quotation or reference, and 4) Modifications or derivative works must clearly indicate changes from the original.

For permissions beyond the scope of this notice, please contact \href{mailto:sebastian.bobadilla.s@gmail.com}{sebastian.bobadilla.s@gmail}

This work is intended to contribute to academic and scientific discourse. While every effort has been made to ensure accuracy, the author makes no warranties about the completeness, reliability, or accuracy of the content. Any views expressed are those of the author and do not necessarily reflect the official policy or position of any institution.

This work is licensed under a Creative Commons Attribution-NonCommercial-NoDerivatives 4.0 International License. Flux AI™ is the property of its respective owner. ChatGPT® and DALL·E® are registered trademarks of OpenAI. Claude™ is a product of Anthropic. All trademarks mentioned are the property of their respective owners. This book is not affiliated with, endorsed by, or sponsored by any of these entities.

Scholars are encouraged to contact the author with substantive feedback, corrections, or suggestions for future editions at \href{mailto:sebastian.bobadilla.s@gmail.com}{sebastian.bobadilla.s@gmail}

    \href{https://bobaseb.github.io/}{Visit the author's website: https://bobaseb.github.io/}

    \href{https://github.com/bobaseb/energetically-coherent-computation}{Manuscript Github}

    \href{https://doi.org/10.17605/OSF.IO/42GXN}{OSF DOI}
    
    London, United Kingdom
    \vspace*{\fill}
\end{center}