\h{Acknowledgments}

This work would not have been possible without the support and inspiration of many individuals. First and foremost, I am deeply grateful to my wife Mérari for her unfailing support and patience with my intellectual pursuits throughout the writing of this book. Our frequent talks on developmental psychology and neuroscience greatly shaped my thinking. Her encouragement made this work possible.

I owe a profound debt to my mother Paty and uncle Rene who nurtured my early curiosity and encouraged exploration of unconventional ideas spanning mysticism and anthropology. Their openness to interdisciplinary thinking helped shape my academic trajectory. I owe a similar gratitude to my sisters, Kiki and Lore, and to both my brothers-in-law Fer and Ivan, for their stimulating conversations on anesthetics, genetics, psychoactive drugs and animal cognition. 

Special thanks go to Simon Moreno, whose reference to theorists like Foucault, Habermas and Bakhtin - that not all processes can be reduced to discursive ones - proved transformative in evolving my perspective on computational theories of mind. I am also grateful to my PhD supervisor Brad Love for engaging thoughtfully with my inquiries into consciousness and directing me to Thomas Nagel's seminal work "A View From Nowhere". Also, I'd like to express my gratitude to Joy Masterson and Tom Edwards at OnCorps for their engaging discussions regarding AI and consciousness. 

The development of this manuscript benefited greatly from advances in artificial intelligence. I wish to acknowledge the teams behind ChatGPT and Claude, including the essential contributions of the annotators and raters whose careful work helped train these systems.

Finally, I am indebted to the many scholars whose work is cited here, as well as those whose ideas have influenced my thinking in ways I may not fully recognize. This work builds upon their foundational contributions to our understanding of mind, consciousness, and human experience.

Any errors or oversights remain entirely my own.