\h{About the Author}

Sebastián Bobadilla Suárez is a cognitive neuroscientist, social anthropologist, and machine learning leader whose work bridges brain science, culture, and cutting-edge technology. He completed his PhD in Cognitive Neuroscience at University College London (UCL), where he worked under the mentorship of Brad Love (Love Lab) and Tali Sharot (Affective Brain Lab). His (post)doctoral research focused on decision-making, heuristics, neural similarity, learning, and categorization, leveraging advanced methods such as fMRI, electrophysiological data analysis, cognitive modeling, and sophisticated statistical/machine learning techniques. During his PhD, Sebastián also spent a year at The Alan Turing Institute, refining his expertise in data science and computational approaches to understanding the mind.

Sebastián’s academic journey began at the Escuela Nacional de Antropología e Historia (ENAH) in Mexico City, where he studied Social Anthropology. Across his degree, he conducted over 120 days of fieldwork in diverse communities, culminating in an intensive 30-day study in Soteapan, Veracruz. His thesis explored the value systems underlying classificatory approaches to psychopathology in the Popoluca-influenced community of Soteapan, which maintains deep cultural ties to nearby Catemaco, Veracruz—a town famous for its witchcraft traditions. His research examined how cultural narratives, magical thinking, and local value systems shape mental health perceptions and behaviors.

Sebastián’s interdisciplinary background now informs his role as Senior Director of Machine Learning at OnCorps, a fintech company at the forefront of decision science and AI-driven innovation. He combines his expertise in cognitive neuroscience, computational modeling, and data science to develop systems that enhance decision-making and drive insights in complex financial contexts.

When not advancing the frontiers of machine learning in financial operations, Sebastián reflects on the intricate connections between culture, cognition, and technology. This book embodies his passion for unraveling the complexities of the human mind and its intersections with the broader world through both scientific and cultural lenses.